---
title: |
  | **Ordinary Differential Equation**
  | **Syllabus**
author: |
  | MTH 321 Sections A & B
  | Fall 2024
  | University of Portland
bibliography: references.bib
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(file.path("R","functions.R"))
```

```{r echo=FALSE}
create_footer()
```

<br>

> See Books & Online Resources Lists for the readings & practice materials.
> 
> The reading materials are not mandatory but it is encouraged.

<br>The "Reading" column in the table below contains page numbers (Pg.) or chapters (ch.) on which it refers to a label in the Books & Online Resources List. For example "Pg. 1-5 [H]" refers to pages 1-5 of the first item in the list, which is the textbook titled "Ordinary Differential Equations: A Primer on Dynamics and Systems".

<br>

## **Topics and Materials**

| **Week** | **Day** | **Topic** | **Worksheet** | **Homework** | **Reading** |
|:-----:|:-----:|:---------------:|:-----:|:-----:|:-----:|
| **1** | Tu 8/27 | Introduction and Orientation to ODEs | Review Algebra and Calculus | - | Syllabus |
|  | Th 8/29 | Modeling Physical Systems,<br>Classification of Equations, & <br>Principles of Solutions | Classify ODEs and Verifying Solutions | - | Ch. 1.1 [T] |
| **2** | Tu 9/3 | 1st-Order ODEs,<br>Existence and Uniqueness, &<br>Analyzing Equilibriums of 1st-Order ODEs | Analyze 1st-Order ODEs Qualitatively | Assigned: Homework 1 | Ch. 1.2 [T] & Ch. 2.1 [T] |
|  | Th 9/5 | Nullclines and Isoclines &<br>Euler's Method for solving 1st-Order ODEs | Solve 1st-Order ODEs Graphically and Numerically | - | Ch. 1.3 [T] & Ch. 3.1 [T] |
| **3** | Tu 9/10 | Separation of Variables for Solving 1st-Order ODEs | Separate the Variables | Assigned: Homework 2 | Ch. 2.2 [T] |
|  | Th 9/12 | Integrating Factors for Solving 1st-Order ODEs | Choose an Integrating Factor | - | Ch. 2.6 [T] |
| **4** | Tu 9/17 | Laplace Transforms for Solving 1st-Order ODEs | Introduce the Laplace Transform | - | Ch. 8.1 [T] & Ch. 8.2 [T] |
|  | Th 9/19 | Bifurcations in One Dimension | Apply Bifurcation Analysis to Physical Systems | - | TBA |
| **5** | Tu 9/24 | _Review_ | Exam 1 Examples | - | Exam 1 Topics |
|  | Th 9/26 | **Exam 1** | - | - | - |
| **6** | Tu 10/1 | Systems of 1st-Order ODEs,<br>Existence and Uniqueness, &<br>Modeling Physical Processes | Interpret 1st-Order System of ODEs | Assigned: Homework 3 | TBA |
|  | Th 10/3 | Analyzing Equilibriums to 1st-Order System of ODEs | Find Equilibriums of 1st-Order System of ODEs | - | - |
| **7** | Tu 10/8 | Linear Transformations & Eigentheory | Solve 1st-Order System of ODEs using Eigentheory | Assigned: Homework 4 | TBA |
|  | Th 10/10 | Stability Analysis &<br>Solutions to 1st-Order System of ODEs | Use Linearization and Stability Analysis | - | TBA |
| **8** | Tu 10/15 | _Fall Vacation_ | - | - | - |
|  | Th 10/17 | _Fall Vacation_ | - | - | - |
| **9** | Tu 10/22 | Eigenvalues and Eigenvectors for solving 1st-Order Linear Systems | Use Distinct or Repeated Eigenvalues | - | TBA |
|  | Th 10/24 | Complex Solutions of 1st-Order Linear Systems | Use Complex Exponentials | - | TBA |
| **10** | Tu 10/29 | _Review_ | Exam 2 Examples | - | Exam 2 Topics |
|  | Th 10/31 | **Exam 2** | - | - | - |
| **11** | Tu 11/5 | Higher Order ODEs,<br>Classification of Equations, &<br>Modeling Physical Processes | Find Homogeneous and Particular Solutions | Assigned: Homework 5 | TBA |
|  | Th 11/7 | Analyzing 2nd-Order Linear ODEs | Use Substitution and Non-Dimensionalization | - | TBA |
| **12** | Tu 11/12 | Undetermined Coefficients for Solving Linear 2nd-Order ODEs | Determine the Undetermined | Assigned: Homework 6 | TBA |
|  | Th 11/14 | Variation of Parameters for Solving Linear 2nd-Order ODEs | Vary the Parameters | - | TBA |
| **13** | Tu 11/19 | Laplace Transforms for Solving Linear 2nd-Order ODEs | Transform the Derivatives | - | - |
|  | Th 11/21 | _Review_ | Exam 3 Examples | - | Exam 3 Topics |
| **14** | Tu 11/26 | **Exam 3** | - | - | - |
|  | Th 11/28 | _Thanksgiving Vacation_ | - | - | - |
| **15** | Tu 12/3 | Bifurcations in Two Dimensions | Apply Bifurcation Theory to Physical Systems | - | TBA |
|  | Th 12/5 | Dynamics and Chaos Theory | Analyze the Lorenz System | - | TBA |
| **16** | Tu 12/11 | Final Exam Section A | - | - | - |
|  | Th 12/12 | Final Exam Section B | - | - | - |

<br>

Along with textbooks [H] and [T], and websites [C] and [P], most of the course materials (contents of worksheets and homework) of each topic was taken from these following sources:

-   Inquiry oriented differential equations (IODE) by @iode2018
-   Differential equations and linear algebra by @strang2014differential
-   Applied differential equations: The primary course by @dobrushkin2022applied
-   Differential Equations by @differentialequationsmitopencourseware

<br>

## **Books & Online Resources Lists**

```{r echo=FALSE}
refs <- bibtex::read.bib("references.bib")
```

*Click on the link to access the resources.*

### Textbooks

[T] `r capture.output(print(refs["trench2013elementary"]))`

### Websites

[C] `r capture.output(print(refs["clontz2022"]))`

[P] `r capture.output(print(refs["paulodenotes"]))`

<br>

## **References**

::: {#refs}
:::

<br>
